Static and Dynamic Bethe-Salpeter Equations in the $T$-Matrix Approximation

### 2022-02-12 Manuscript/Tmatrix.tex
res
water

Due to the frequency-independent nature of the static BSE, it is well known that one cannot access double (and higher) excitations.
\cite{Loos_2019,Romaniello_2009b,Sangalli_2011,Loos_2020h,Authier_2020,Monino_2021}
In order to go beyond the static approximation, it is possible to consider, within the dynamical TDA (dTDA) that neglects the frequency dependence of the coupling block $\bB{}{}$, the dynamical version of the BSE (dBSE). \cite{Strinati_1988,Romaniello_2009b,Loos_2020h}
In this case, one must solve the (non-linear) dynamical eigenvalue problem
\begin{equation}
\label{eq:dBSE}
	\begin{pmatrix}
		\bA{}{\dBSE}(\Om{S}{})	&	\bB{}{\BSE}	\\
		-\bB{}{\BSE}	&	-\bA{}{\dBSE}(-\Om{S}{})	\\
	\end{pmatrix}
	\cdot
	\begin{pmatrix}
		\bX{S}{\dBSE}	\\
		\bY{S}{\dBSE}	\\
	\end{pmatrix}
	=
	\Om{S}{}
	\begin{pmatrix}
		\bX{S}{\dBSE}	\\
		\bY{S}{\dBSE}	\\
	\end{pmatrix}
\end{equation}
with 
\begin{equation}
	A_{ia,jb}^{\dBSE}(\omega) = \delta_{ij} \delta_{ab} (\e{a}{\GT} - \e{i}{\GT}) + \mel{ib}{}{aj} - \widetilde{T}_{ib,aj}(\omega)
\end{equation}
where, following Strinati's seminal work, \cite{Strinati_1988} one can derive the following expression for the elements of the dynamical $T$ matrix
\begin{equation}
\label{eq:dT}
\begin{split}
	\widetilde{T}_{pq,rs}(\omega) 
		& = \sum_{n} \frac{\braket*{pq}{\chi_n^{N+2}}\braket*{rs}{\chi_n^{N+2}}}{\omega - \Om{n}{N+2} + (\e{i}{\GT} + \e{j}{\GT}) + i\eta}
		\\
		& + \sum_{n} \frac{\braket*{pq}{\chi_n^{N-2}}\braket*{rs}{\chi_n^{N-2}}}{\omega + \Om{n}{N-2} - (\e{a}{\GT} + \e{b}{\GT}) + i\eta}
\end{split}
\end{equation}
from which, one can check that we recover the static expression \eqref{eq:T} in the limit $\Om{n}{N\pm2} \to \infty$.
Equation \eqref{eq:dT} highlights the interesting dynamical structure of the $T$ matrix, where, similarly to the dBSE@$GW$ scheme, \cite{Strinati_1988,Romaniello_2009b,Loos_2020h} the 2h2p configurations are downfolded on the 1h1p configurations. \cite{Bintrim_2021b}

@@

In terms of computational cost, the overall scaling of BSE@$GT$ is equivalent to BSE@$GW$ as they both correspond to seeking the lowest eigenvalues of a matrix of size $(2\Nocc\Nvir \times 2\Nocc\Nvir)$. 
Searching iteratively for the lowest eigenstates can be routinely performed via Davidson's algorithm with a $\order*{\Norb^4}$ computational cost. \cite{Davidson_1975}
The cost of the dynamical correction, which is thoroughly discussed in Ref.~\onlinecite{Loos_2020h}, is more expensive but is again equivalent in both formalisms.
The computational cost associated with the computation of the $T$-matrix and the screening $W$ both scale as $\order*{\Norb^6}$ as one must obtain, respectively, all the eigenvalues and eigenvectors of the pp-RPA and ph-RPA problems.
However, the prefactor of the pp-RPA calculation is significantly larger than its ph-RPA counterpart due to the larger size of the pp-RPA matrices and its non-Hermitian nature. \cite{Peng_2013,Scuseria_2013,Yang_2013,Yang_2013b,Yang_2014a,Zhang_2015,Zhang_2016}
Moreover, within the $T$-matrix formalism, one must compute both the singlet and triplet contributions of the $T$-matrix, while for singlet states, only the singlet contribution of $W$ contributes to the self-energy.
Although similar approaches remain to be developed for the $T$-matrix formalism, contour deformation and density fitting techniques can be efficiently implemented in the case of $GW$ to reduce the scaling to $\order*{\Norb^3}$. \cite{Duchemin_2019,Duchemin_2020,Duchemin_2021}

@@

%%% FIGURE 3 %%%
\begin{figure*}
	\includegraphics[width=0.4\linewidth]{H2_dBSE1}
	\hspace{0.1\linewidth}
	\includegraphics[width=0.4\linewidth]{H2_dBSE3}
	\caption{
	Error with respect to FCI for the lowest singlet (left) and the lowest triplet (right) excitation energies of \ce{H2} as a function of the internuclear distance $R_{\ce{H-H}}$ (in \si{\angstrom}) computed within the static scheme (BSE@$G_0W_0$ and BSE@$G_0T_0$) and the dynamically-corrected scheme (dBSE@$G_0W_0$ and dBSE@$G_0T_0$) .
	The cc-pVTZ basis is employed for all calculations.
	Raw data are reported in {\SupInf}.}
	\label{fig:H2_dBSE}
\end{figure*}
%%% %%% %%% %%%

As a first didactical example, we consider the lowest singlet and triplet excited states of the hydrogen molecule \ce{H2} and the variation of their respective vertical transition energies upon dissociation.
The excitation energies associated with these low-lying excited states are represented in Fig.~\ref{fig:H2} as a function of the internuclear distance $R_{\ce{H-H}}$ at the FCI (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels with the cc-pVTZ basis.
The variation of the HOMO and LUMO quasiparticle energies as well as HOMO-LUMO gap computed at the $G_0W_0$ and $G_0T_0$ levels is depicted in Fig.~\ref{fig:H2_gap}
This shows that, as already observed in the Hubbard dimer \cite{Romaniello_2012} and in molecular systems, \cite{Zhang_2017} the $G_0W_0$ and $G_0T_0$ quasiparticle energies are similar near the Fermi level.

@@

%%% FIGURE 4 %%%
\begin{figure*}
	\includegraphics[width=\textwidth]{BeH2}
	\caption{Singlet (left) and triplet (right) excitation energies (in \si{\eV}) of \ce{BeH2} as a function of the distance $R_{\ce{Be-H}}$ (in \si{\angstrom}) computed at the FCI (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels.
	The dynamically-corrected BSE excitation energies are represented as thin lines for dBSE@$G_0W_0$ (blue), and dBSE@$G_0T_0$ (red) with the cc-pVDZ basis.
	Raw data are reported in {\SupInf}.}
	\label{fig:BeH2}
\end{figure*}
%%% %%% %%% %%%

@@

As a second example, we consider the symmetric dissociation of the linear molecule beryllium hydride (\ce{BeH2}), a system for which one can assume that the screening may play a more important role than in the previous example.
The variation of the lowest singlet and triplet excitation energies as a function of the distance $R_{\ce{Be-H}}$ is shown in Fig.~\ref{fig:BeH2}, while the quasiparticle energies of the frontier orbitals and the associated (fundamental) gap computed at the $G_0W_0$ and $G_0T_0$ levels is depicted in Fig.~\ref{fig:BeH2_gap}.
Again, one notes that the $G_0W_0$ and $G_0T_0$ quasiparticle energies are very similar near the Fermi level.
Therefore, one can safely assume that any significant variation of the excitation energies computed within the $GW$- and $GT$-based formalisms originates mainly from their distinct kernel.
The excitation energies computed with the dynamical schemes, dBSE@$G_0W_0$ and dBSE@$G_0T_0$, are reported as thin solid lines.
Here, one can show that dynamical corrections improves in most cases the agreement between BSE and FCI.
All calculations are performed with the cc-pVDZ basis.

@@

%%%%%%%%%%%%%%%%%%%%%%
\subsection{Molecules at equilibrium}
\label{sec:mol}
%%%%%%%%%%%%%%%%%%%%%%

Table \ref{tab:mol} reports singlet and triplet vertical excitation energies for various molecular systems at equilibrium geometry.
In addition to the BSE-based models studied in the present manuscript, we have selected well-known methods, namely CIS, CIS(D), TDHF, and FCI (taken as reference).

%%% TABLE I %%%
\begin{table*}
	\caption{Singlet and triplet excitation energies (in \si{\eV}) of various molecular systems at equilibrium geometry computed at various levels of theory with the aug-cc-pVDZ basis set.
	The corresponding equilibrium geometries as well as the reference FCI values have been extracted from the QUEST database. \cite{Veril_2021}}
	\label{tab:mol}
	\begin{ruledtabular}
		\begin{tabular}{llccccccccc}
					&			&		&	\mc{8}{c}{Methods}																\\
			\cline{4-11}
			Mol.	&	State	&	Nature						&	CIS		&	CIS(D)	&	TDHF	&	BSE@$G_0W_0$	&	dBSE@$G_0W_0$	&	BSE@$G_0T_0$	&	dBSE@$G_0T_0$	&	FCI	\\
			\hline
			\ce{H2O}	&	$^1B_1(n \to 3s)$		&	Ryd.	&	8.66	&	6.61	&	8.61	&	7.70	&	7.62	&	6.84	&	6.80	&	7.53\\
						&	$^1A_2(n \to 3p)$		&	Ryd.	&	10.34	&	8.33	&	10.30	&	9.41	&	9.34	&	8.60	&	8.56	&	9.32\\
						&	$^3B_1(n \to 3s)$		&	Ryd.	&	7.98	&	6.69	&	7.86	&	7.23	&	7.09	&	6.30	&	6.23	&	7.14\\
						&	$^3A_2(n \to 3p)$		&	Ryd.	&	10.01	&	8.70	&	9.89	&	9.22	&	9.11	&	8.36	&	8.29	&	9.14\\
			\ce{HCl}	&	$^1\Pi$					&	CT		&	8.36	&	7.87	&	8.31	&	8.04	&	7.95	&	7.42	&	7.38	&	7.82\\
			\ce{HC#CH}	&	$^1\Sigma_u^-(\pps)$	&	Val.	&	6.28	&	6.29	&	5.91	&	7.27	&	6.96	&	5.64	&	5.55	&	7.20\\
						&	$^1\Delta_u(\pps)$		&	Val.	&	6.62	&	6.97	&	6.44	&	7.61	&	7.33	&	5.87	&	5.81	&	7.51\\
						&	$^3\Sigma_u^+(\pps)$	&	Val.	&	4.52	&	5.75	&	2.19	&	5.63	&	5.12	&	4.02	&	3.83	&	5.50\\
						&	$^3\Delta_u(\pps)$		&	Val.	&	5.45	&	6.65	&	4.52	&	6.52	&	6.13	&	4.87	&	4.74	&	6.46\\
			\ce{H2C=NH}	&	$^1A''(\nps)$			&	Val.	&	5.86	&	4.46	&	5.69	&	6.16	&	5.85	&	4.12	&	4.04	&	5.25\\
						&	$^3A''(\nps)$			&	Val.	&	4.71	&	4.72	&	4.39	&	5.49	&	4.96	&	3.25	&	3.11	&	4.63\\
		\end{tabular}
	\end{ruledtabular}
\end{table*}
%%% %%% %%% %%%

%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
\label{sec:ccl}
%%%%%%%%%%%%%%%%%%%%%%
To conclude, the BSE@$GT$ formalism seems to be, overall, less accurate than BSE@$GW$ in the context of the computation of molecular excitation energies.
However, it still outperforms conventional methods such CIS and TDHF.
It would be interesting to investigate its performance for the computation of ground-state correlation energies within the adiabatic connection fluctuation dissipation formalism where BSE@$GW$ has been shown to be particularly outstanding. \cite{Maggio_2016,Holzer_2018b,Loos_2020e}
The combination of $GT$ and $GW$ via the range separation of the Coulomb operator to avoid double counting of the low-order diagrams is also a promising avenue.
Work along these lines are currently under progress.
Finally, the unrestricted and spin-flip extensions of the present formalism is currently developed.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgements}
%The authors thank Roberto Orlando for useful discussions.
PFL thanks the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (Grant agreement No.~863481) for funding.
This project has also received financial support from the CNRS through the 80|Prime program and has been supported through the EUR grant NanoX ANR-17-EURE-0009 in the framework of the ``Programme des Investissements d’Avenir''.
\end{acknowledgements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%
\onecolumngrid
\appendix
%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{BSE with a dynamical $T$-matrix kernel}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

Due to the frequency-independent nature of the static BSE, it is well known that one cannot access double (and higher) excitations.
\cite{Loos_2019,Romaniello_2009b,Sangalli_2011,Loos_2020h,Authier_2020,Monino_2021}
In order to go beyond the static approximation, it is possible to consider, within the dynamical TDA (dTDA) that neglects the frequency dependence of the coupling block $\bB{}{}$, the dynamical version of the BSE (dBSE). \cite{Strinati_1988,Romaniello_2009b,Loos_2020h}
In this case, one must solve the (non-linear) dynamical eigenvalue problem
\begin{equation}
\label{eq:dBSE}
	\begin{pmatrix}
		\bA{}{\dBSE}(\Om{S}{})	&	\bB{}{\BSE}	\\
		-\bB{}{\BSE}	&	-\bA{}{\dBSE}(-\Om{S}{})	\\
	\end{pmatrix}
	\cdot
	\begin{pmatrix}
		\bX{S}{\dBSE}	\\
		\bY{S}{\dBSE}	\\
	\end{pmatrix}
	=
	\Om{S}{}
	\begin{pmatrix}
		\bX{S}{\dBSE}	\\
		\bY{S}{\dBSE}	\\
	\end{pmatrix}
\end{equation}
with 
\begin{equation}
	A_{ia,jb}^{\dBSE}(\omega) = \delta_{ij} \delta_{ab} (\e{a}{\GT} - \e{i}{\GT}) + \mel{ib}{}{aj} - \widetilde{T}_{ib,aj}(\omega)
\end{equation}
where, following Strinati's seminal work, \cite{Strinati_1988} one can derive the following expression for the elements of the dynamical $T$ matrix
\begin{equation}
\label{eq:dT}
\begin{split}
	\widetilde{T}_{pq,rs}(\omega) 
		& = \sum_{n} \frac{\braket*{pq}{\chi_n^{N+2}}\braket*{rs}{\chi_n^{N+2}}}{\omega - \Om{n}{N+2} + (\e{i}{\GT} + \e{j}{\GT}) + i\eta}
		\\
		& + \sum_{n} \frac{\braket*{pq}{\chi_n^{N-2}}\braket*{rs}{\chi_n^{N-2}}}{\omega + \Om{n}{N-2} - (\e{a}{\GT} + \e{b}{\GT}) + i\eta}
\end{split}
\end{equation}
from which, one can check that we recover the static expression \eqref{eq:T} in the limit $\Om{n}{N\pm2} \to \infty$.
Equation \eqref{eq:dT} highlights the interesting dynamical structure of the $T$ matrix, where, similarly to the dBSE@$GW$ scheme, \cite{Strinati_1988,Romaniello_2009b,Loos_2020h} the 2h2p configurations are downfolded on the 1h1p configurations. \cite{Bintrim_2021b}
Additional details about the derivation of Eq.~\eqref{eq:dT} are reported in Appendix \ref{app:dBSE}.

@@

In terms of computational cost, the overall scaling of BSE@$GT$ is equivalent to BSE@$GW$ as they both correspond to seeking the lowest eigenvalues of a matrix of size $(2\Nocc\Nvir \times 2\Nocc\Nvir)$. 
Searching iteratively for the lowest eigenstates can be routinely performed via Davidson's algorithm with a $\order*{\Norb^4}$ computational cost. \cite{Davidson_1975}
The cost of the dynamical correction, which is thoroughly discussed in Ref.~\onlinecite{Loos_2020h}, is more expensive but is again equivalent in both formalisms.
The computational cost associated with the computation of the $T$-matrix and the screening $W$ both scale as $\order*{\Norb^6}$ as one must obtain, respectively, all the eigenvalues and eigenvectors of the pp-RPA and ph-RPA problems.
However, the prefactor of the pp-RPA calculation is significantly larger than its ph-RPA counterpart due to the larger size of the pp-RPA matrices and its non-Hermitian nature. \cite{Peng_2013,Scuseria_2013,Yang_2013,Yang_2013b,Yang_2014a,Zhang_2015,Zhang_2016}
Moreover, within the $T$-matrix formalism, one must compute both the singlet and triplet contributions of the $T$-matrix, while for singlet states, only the singlet part of $W$ is required.
Although similar approaches remain to be developed for the $T$-matrix formalism, contour deformation and density fitting techniques can be efficiently implemented in the case of $GW$ to reduce the scaling to $\order*{\Norb^3}$. \cite{Duchemin_2019,Duchemin_2020,Duchemin_2021}

@@

%%% FIGURE 3 %%%
\begin{figure*}
	\includegraphics[width=0.4\linewidth]{H2_dBSE1}
	\hspace{0.1\linewidth}
	\includegraphics[width=0.4\linewidth]{H2_dBSE3}
	\caption{
	Error with respect to FCI for the lowest singlet (left) and the lowest triplet (right) excitation energies of \ce{H2} as a function of the internuclear distance $R_{\ce{H-H}}$ (in \si{\angstrom}) computed within the static schemes (BSE@$G_0W_0$ and BSE@$G_0T_0$) and the dynamically-corrected schemes (dBSE@$G_0W_0$ and dBSE@$G_0T_0$) .
	The cc-pVTZ basis is employed for all calculations.
	Raw data are reported in {\SupInf}.}
	\label{fig:H2_dBSE}
\end{figure*}
%%% %%% %%% %%%

As a first didactical example, we consider the lowest singlet and triplet excited states of the hydrogen molecule \ce{H2} and the variation of their respective vertical transition energies upon dissociation.
The excitation energies associated with these low-lying excited states are represented in Fig.~\ref{fig:H2} as a function of the internuclear distance $R_{\ce{H-H}}$ at the FCI (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels with the cc-pVTZ basis.
The variation of the HOMO and LUMO quasiparticle energies as well as HOMO-LUMO gap computed at the $G_0W_0$ and $G_0T_0$ levels is depicted in Fig.~\ref{fig:H2_gap}.
This shows that, as already observed in the Hubbard dimer \cite{Romaniello_2012} and in molecular systems, \cite{Zhang_2017} the $G_0W_0$ and $G_0T_0$ quasiparticle energies are similar near the Fermi level.

@@

%%% FIGURE 4 %%%
\begin{figure*}
	\includegraphics[width=\textwidth]{BeH2}
	\caption{Singlet (left) and triplet (right) excitation energies (in \si{\eV}) of \ce{BeH2} as a function of the distance $R_{\ce{Be-H}}$ (in \si{\angstrom}) computed at the FCI (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels with the cc-pVDZ basis.
	The dynamically-corrected BSE excitation energies are represented as thin lines for dBSE@$G_0W_0$ (blue) and dBSE@$G_0T_0$ (red).
	Raw data are reported in {\SupInf}.}
	\label{fig:BeH2}
\end{figure*}
%%% %%% %%% %%%

@@

As a second example, we consider the symmetric dissociation of the linear molecule beryllium hydride (\ce{BeH2}), a system for which one can assume that the screening plays a more important role than in the previous example.
The variation of the lowest singlet and triplet excitation energies as a function of the distance $R_{\ce{Be-H}}$ is shown in Fig.~\ref{fig:BeH2}, while the quasiparticle energies of the frontier orbitals and the associated (fundamental) gap computed at the $G_0W_0$ and $G_0T_0$ levels is depicted in Fig.~\ref{fig:BeH2_gap}.
Again, one notes that the $G_0W_0$ and $G_0T_0$ quasiparticle energies are very similar near the Fermi level.
Therefore, one can safely assume that any significant variation of the excitation energies computed within the $GW$- and $GT$-based formalisms originates mainly from their distinct kernel.
The excitation energies computed with the dynamical schemes, dBSE@$G_0W_0$ and dBSE@$G_0T_0$, are reported as thin solid lines.
Here, one can show that dynamical corrections improves in most cases the agreement between BSE and FCI.
All calculations are performed with the cc-pVDZ basis.

@@

%%%%%%%%%%%%%%%%%%%%%%
\subsection{Excited states of water}
\label{sec:H2O}
%%%%%%%%%%%%%%%%%%%%%%

%%% FIGURE 6 %%%
\begin{figure*}
	\includegraphics[width=\linewidth]{H2O}
	\caption{Error with respect to FCI for the singlet (left) and triplet (right) excitation energies (in \si{\eV}) of \ce{H2O} at equilibrium geometry computed at various levels of theory with the aug-cc-pVDZ basis.
	The geometry as well as the reference FCI values have been extracted from the QUEST database. \cite{Veril_2021}
	Raw data are reported in {\SupInf}.}
	\label{fig:H2O}
\end{figure*}
%%% %%% %%% %%%

As a third and final example, we compute the excitation energies associated with the two lowest singlet and two lowest triplet excited states of water at equilibrium geometry (see Fig.~\ref{fig:H2O}).
Note that all these excited states are of Rydberg nature and correspond to $n \to 3s$ and $n \to 3p$ transitions for the $B_1$ and $A_2$ states, respectively.
In addition to the BSE-based models studied in the present manuscript, we have selected well-known wave function methods, namely CIS, CIS(D), TDHF, and FCI (taken as reference) and computed the excitation energies for these transitions.
Two key observations can be made:
i) BSE@$G_0W_0$ is by far the best performer with a slight overestimation of the order of \SI{0.1}{eV} (as compared to FCI);
ii) BSE@$G_0T_0$ systematically underestimates the excitation energies [similarly to CIS(D)] and outperforms CIS, CIS(D) and TDHF for the singlet states only. 
These general trends are also observed for other systems and they nicely evidence the crucial role of the screening in $GW$, hinting that a screened version of the $T$-matrix formalism as proposed in Ref.~\onlinecite{Romaniello_2012} might be a promising way for improvement.

%%% TABLE I %%%
%\begin{table*}
%	\caption{Singlet and triplet excitation energies (in \si{\eV}) of various molecular systems at equilibrium geometry computed at various levels of theory with the aug-cc-pVDZ basis set.
%	The corresponding equilibrium geometries as well as the reference FCI values have been extracted from the QUEST database. \cite{Veril_2021}}
%	\label{tab:mol}
%	\begin{ruledtabular}
%		\begin{tabular}{llccccccccc}
%					&			&		&	\mc{8}{c}{Methods}																\\
%			\cline{4-11}
%			Mol.	&	State	&	Nature						&	CIS		&	CIS(D)	&	TDHF	&	BSE@$G_0W_0$	&	dBSE@$G_0W_0$	&	BSE@$G_0T_0$	&	dBSE@$G_0T_0$	&	FCI	\\
%			\hline
%			\ce{H2O}	&	$^1B_1(n \to 3s)$		&	Ryd.	&	8.66	&	6.61	&	8.61	&	7.70	&	7.62	&	6.84	&	6.80	&	7.53\\
%						&	$^1A_2(n \to 3p)$		&	Ryd.	&	10.34	&	8.33	&	10.30	&	9.41	&	9.34	&	8.60	&	8.56	&	9.32\\
%						&	$^3B_1(n \to 3s)$		&	Ryd.	&	7.98	&	6.69	&	7.86	&	7.23	&	7.09	&	6.30	&	6.23	&	7.14\\
%						&	$^3A_2(n \to 3p)$		&	Ryd.	&	10.01	&	8.70	&	9.89	&	9.22	&	9.11	&	8.36	&	8.29	&	9.14\\
%			\ce{HCl}	&	$^1\Pi$					&	CT		&	8.36	&	7.87	&	8.31	&	8.04	&	7.95	&	7.42	&	7.38	&	7.82\\
%			\ce{HC#CH}	&	$^1\Sigma_u^-(\pps)$	&	Val.	&	6.28	&	6.29	&	5.91	&	7.27	&	6.96	&	5.64	&	5.55	&	7.20\\
%						&	$^1\Delta_u(\pps)$		&	Val.	&	6.62	&	6.97	&	6.44	&	7.61	&	7.33	&	5.87	&	5.81	&	7.51\\
%						&	$^3\Sigma_u^+(\pps)$	&	Val.	&	4.52	&	5.75	&	2.19	&	5.63	&	5.12	&	4.02	&	3.83	&	5.50\\
%						&	$^3\Delta_u(\pps)$		&	Val.	&	5.45	&	6.65	&	4.52	&	6.52	&	6.13	&	4.87	&	4.74	&	6.46\\
%			\ce{H2C=NH}	&	$^1A''(\nps)$			&	Val.	&	5.86	&	4.46	&	5.69	&	6.16	&	5.85	&	4.12	&	4.04	&	5.25\\
%						&	$^3A''(\nps)$			&	Val.	&	4.71	&	4.72	&	4.39	&	5.49	&	4.96	&	3.25	&	3.11	&	4.63\\
%		\end{tabular}
%	\end{ruledtabular}
%\end{table*}
%%% %%% %%% %%%

%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
\label{sec:ccl}
%%%%%%%%%%%%%%%%%%%%%%
To conclude, the BSE@$GT$ formalism seems to be, overall, less accurate than BSE@$GW$ in the context of the computation of molecular excitation energies.
However, it still outperforms conventional methods such CIS and TDHF for singlet states.
It would be interesting to investigate its performance for the computation of ground-state correlation energies within the adiabatic connection fluctuation dissipation formalism where BSE@$GW$ has been shown to be particularly outstanding. \cite{Maggio_2016,Holzer_2018b,Loos_2020e}
The combination of $GT$ and $GW$ via the range separation of the Coulomb operator to avoid double counting of the low-order diagrams is also a promising avenue.
Work along these lines are currently under progress.
Finally, the unrestricted and spin-flip extensions of the present formalism are currently being developed.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgements}
The authors thank Roberto Orlando for useful discussions.
PFL thanks the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (Grant agreement No.~863481) for funding.
This project has also received financial support from the CNRS through the 80|Prime program and has been supported through the EUR grant NanoX ANR-17-EURE-0009 in the framework of the ``Programme des Investissements d’Avenir''.
\end{acknowledgements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%
\onecolumngrid
\appendix
%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{BSE with a dynamical $T$-matrix kernel}
\label{app:dBSE}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
